A 3d curvilinear skeletonization algorithm with application to path tracing

### 2012-09-14 skeleton_and_pathtracing.tex
Small change

\title{A 3d curvilinear skeletonization algorithm with application to path tracing}
\author{John Chaussard\inst{1} \and Laurent No\"{e}l\inst{2} \and Venceslas Biri\inst{2} \and Michel Couprie\inst{2}\thanks{This work has been partially supported by the \quotes{ANR-2010-BLAN-0205 KIDICO} project}}
\institute{Universit\'{e} Paris 13, Sorbonne Paris Cit\'{e}, LAGA, CNRS(UMR 7539), \\ F-93430, Villetaneuse, France \\ \email{chaussard@math.univ-paris13.fr}
\and
Universit\'{e} Paris Est, LIGM, A3SI-ESIEE \\ 2, boulevard Blaise Pascal, Cit\'{e} DESCARTES \\ BP 99  93162 Noisy le Grand CEDEX, France \\ \email{laurent.noel@esiee.fr, v.biri@esiee.fr, michel.couprie@esiee.fr}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                        %
%                   INTRODUCTION                         %
%                                                        %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec::intro}
\begin{figure}[t]
\begin{center}
\begin{tabular}{cc}
	\myincludegraphics{0.60\textwidth}{dgci_ray_corridor.png} &
	\myincludegraphics{0.40\textwidth}{dgci_compare_door.png}
\end{tabular}
\caption{Images $a$ and $b$ shows some rays of the path tracing guided by the material of the objects (image $a$) or our skeleton based method (image $b$). Images $c$ and $d$ point out the noise reduction between the classic path tracing (image $c$) and our method (image $d$)}
\end{center}
\end{figure}
Path tracing algorithms are able to render photorealistic images from a scene description by simulating light propagation. The photorealistic aspect is achieved by simulating diffusion of light: elements of the scene which are illuminated by a light source can cast part of the light they receive. Consequently, parts of the scene which are not directly illuminated by any light source actually receive light, thus giving a realistic effect of light diffusion to the resulting image.

@@

@@

\begin{algorithm}[ht!]
\label{algo::pardircollapse_v0}
\SetKwFor{ForAll}{for all}{do}{end}
\caption[ParDirCollapse]{$ParDirCollapse(X,W,\ell)$}
\KwData{A cubical complex $\complex{n}{X}$, a subcomplex
  $\subcomplex{W}{X}$ which represents faces of $X$ which should not
  be removed, and $\ell \in \Nset$, the number of layers of free faces
  which should be removed from $X$} 
\KwResult{A cubical complex}
\lnl{pc:01}\While{there exists free faces in $X \setminus W$ and $\ell > 0$}{
\lnl{pc:02}  $L=\border{X}^-$\;
\lnl{pc:03}  \For{$t=0 \rightarrow n-1$}{
\lnl{pc:04}    \For{$s=0 \rightarrow 1$}{
\lnl{pc:05}      \For{$d=n \rightarrow 1$}{
\lnl{pc:06}        $E=\{(f,g)$ free for $X \suchthat g \notin W,$\\
                      $\;$~~~~~~~$\type{f,g}=t,$ $\orient{f,g}=s,$ $\mydim{f}=d\}$\;
\lnl{pc:07}        $G=\{(f,g) \in E \suchthat f \in L$ and $g \in L\}$\;
\lnl{pc:08}        $X=X \setminus G$\;
                 }
               }
             }
\lnl{pc:09}  $l = l-1$\;
	   }
\lnl{pc:10} \Return $X$\;
\end{algorithm}

\begin{figure}[htp]
\begin{center}
\begin{tabular}{ccccc}
	\myincludegraphics{0.19\textwidth}{invader.pdf} &
	\myincludegraphics{0.19\textwidth}{invader_step1_2.pdf} &
	\myincludegraphics{0.19\textwidth}{invader_step2_2.pdf} &
	\myincludegraphics{0.19\textwidth}{invader_step3.pdf} &
	\myincludegraphics{0.19\textwidth}{invader_step4.pdf} \\
\end{tabular}
\caption[Four first iterations of Alg.~\ref{algo::pardircollapse_v0}]{\label{fig::example_algo} \textbf{Four first iterations of Alg.~\ref{algo::pardircollapse_v0}} running on the left-most shape.}
\end{center}
\end{figure}

Different definitions of orientation and direction can be given, each corresponding to a different order of free faces removal in the complex and leading to different results.
Algorithm~\ref{algo::pardircollapse_v0} can be implemented to run in linear time complexity (proportionally to the number of faces in the complex). Indeed, checking if a face is free or not may be easily done in constant time. Moreover, when a free pair $(f,g)$ is removed from the input complex, it is sufficient to scan the faces contained in $f$ in order to find new free faces.

\section{Aspect preservation during thinning: a parameter-free method}
\label{sec::aspect_no_param}
As previously said, our goal is to use the skeleton of the voids of a scene in order to guide light rays from the camera of the scene towards the light. Moreover, this skeleton needs to capture the main geometrical features of the original scene. For example, if the input is a corridor (the void of the corridor), then the skeleton should be a line following the main direction of the corridor.

@@

\begin{figure}[htp]
\begin{center}
\begin{tabular}{cccc}
	\myincludegraphics{0.22\textwidth}{fish.pdf} &
	\myincludegraphics{0.22\textwidth}{fishd.pdf} &
	\myincludegraphics{0.22\textwidth}{fishdd.pdf} &
	\myincludegraphics{0.22\textwidth}{fishcenter.pdf} \\
\end{tabular}
\caption[Example of opening and decenterness map]{\label{fig::globalopening} \textbf{Example of opening and decenterness map - } From left to right: a shape $S \subset \Zset^2$ (in gray), $\Dist1{S}$, $\DD1{S}$ and $\decent{S}$ (low values have dark colour).}
\end{center}
\end{figure}

\subsection{Parameter-free thinning based on the lifespan, opening function and decenterness}
As previously said, we add edges to the set $W$ of Alg.~\ref{algo::pardircollapse_v0} in order to retain, in the resulting curvilinear skeleton, important edges from the original object. Given a cubical complex $X$, if an edge of $X$ has a high decenterness value for $X$, then it is probably located too close to the border of $X$ and does not represent an interesting geometrical feature to preserve.
%TODO ref vers image de decenterness
On the other hand, if an edge has a high lifespan for $X$, then it means it was not removed quickly, after becoming a facet, by the thinning algorithm and might represent some precious geometrical information on the original object. An idea would be to keep, during thinning, all edges whose lifespan is superior to the decenterness value. Unfortunately, this strategy produces skeletons with many spurious branches in surfacic areas of the original object.

@@

\begin{algorithm}[ht]
\label{algo::3d_curvskel}
\caption[CurvilinearSkeleton]{$CurvilinearSkeleton(X)$}
\KwData{A cubical complex $\complex{3}{X}$}
\KwResult{A cubical complex $\complex{3}{Y}$}
\lnl{curvskel:01} $W=\{f \in X | \lifespan{f}{X} > \cpldecent{X}(f) + \birth{f}{X} - \cplDist1{X}(f)$ and $\mydim{f}=1\}$\;
\Return $ParDirCollapse(X,W,+\infty)$\;
\end{algorithm}

@@

Algorithm \ref{algo::3d_curvskel} allows to obtain a filtered curvilinear skeleton from a three dimensional complex. The results presented in Fig.~\ref{fig::result_skel} show that the skeletons contain the main geometrical information from the input shapes, and do not contain spurious branches.

\begin{figure}[htp]
\begin{center}
\begin{tabular}{cc|cc}
	\myincludegraphics{0.18\textwidth}{hand2.jpg} &
	\myincludegraphics{0.18\textwidth}{hand_curvskel.jpg} &
	\myincludegraphics{0.24\textwidth}{neptune.jpg} &
	\myincludegraphics{0.24\textwidth}{neptune_curvskel.jpg} \\
\end{tabular}
\caption[Results of algorithm \ref{algo::3d_curvskel}]{\label{fig::result_skel} \textbf{Results of algorithm \ref{algo::3d_curvskel}} for two shapes: a hand (left) and a statue (right). In each pair, the rightmost image represents the skeleton.}
\end{center}
\end{figure}

>>>>

\title{A 3d curvilinear skeletonization algorithm with application to path tracing}
\author{John Chaussard\inst{1} \and Laurent No\"{e}l\inst{2} \and Venceslas Biri\inst{2} \and Michel Couprie\inst{2}\thanks{This work has been partially supported by the \quotes{ANR-2010-BLAN-0205 KIDICO} project}}
\institute{Universit\'{e} Paris 13, Sorbonne Paris Cit\'{e}, LAGA, CNRS(UMR 7539), \\ F-93430, Villetaneuse, France \\ \email{chaussard@math.univ-paris13.fr}
\and
Universit\'{e} Paris Est, LIGM, A3SI-ESIEE \\ 2, boulevard Blaise Pascal, 93162 Noisy le Grand CEDEX, France \\ \email{laurent.noel@esiee.fr, v.biri@esiee.fr, michel.couprie@esiee.fr}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                        %
%                   INTRODUCTION                         %
%                                                        %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec::intro}

Path tracing algorithms are able to render photorealistic images from a scene description by simulating light propagation. The photorealistic aspect is achieved by simulating diffusion of light: elements of the scene which are illuminated by a light source can cast part of the light they receive. Consequently, parts of the scene which are not directly illuminated by any light source actually receive light, thus giving a realistic effect of light diffusion to the resulting image.

@@

\begin{figure}[tb]
\begin{center}
\begin{tabular}{cc}
	\myincludegraphics{0.60\textwidth}{dgci_ray_corridor.png} &
	\myincludegraphics{0.40\textwidth}{dgci_compare_door.png}
\end{tabular}
\caption{Images $a$ and $b$ shows some rays of the path tracing guided by the material of the objects (image $a$) or our skeleton based method (image $b$). Images $c$ and $d$ point out the noise reduction between the classic path tracing (image $c$) and our method (image $d$)}
\end{center}
\end{figure}

@@

\begin{algorithm}[tb]
\label{algo::pardircollapse_v0}
\SetKwFor{ForAll}{for all}{do}{end}
\caption[ParDirCollapse]{$ParDirCollapse(X,W,\ell)$}
\KwData{A cubical complex $\complex{n}{X}$, a subcomplex
  $\subcomplex{W}{X}$ which represents faces of $X$ which should not
  be removed, and $\ell \in \Nset$, the number of layers of free faces
  which should be removed from $X$} 
\KwResult{A cubical complex}
\lnl{pc:01}\While{there exists free faces in $X \setminus W$ and $\ell > 0$}{
\lnl{pc:02}  $L=\border{X}^-$\;
\lnl{pc:03}  \For{$t=0 \rightarrow n-1$}{
\lnl{pc:04}    \For{$s=0 \rightarrow 1$}{
\lnl{pc:05}      \For{$d=n \rightarrow 1$}{
\lnl{pc:06}        $E=\{(f,g)$ free for $X \suchthat g \notin W,$\\
                      $\;$~~~~~~~$\type{f,g}=t,$ $\orient{f,g}=s,$ $\mydim{f}=d\}$\;
\lnl{pc:07}        $G=\{(f,g) \in E \suchthat f \in L$ and $g \in L\}$\;
\lnl{pc:08}        $X=X \setminus G$\;
                 }
               }
             }
\lnl{pc:09}  $l = l-1$\;
	   }
\lnl{pc:10} \Return $X$\;
\end{algorithm}

\begin{figure}[tb]
\begin{center}
\begin{tabular}{ccccc}
	\myincludegraphics{0.19\textwidth}{invader.pdf} &
	\myincludegraphics{0.19\textwidth}{invader_step1_2.pdf} &
	\myincludegraphics{0.19\textwidth}{invader_step2_2.pdf} &
	\myincludegraphics{0.19\textwidth}{invader_step3.pdf} &
	\myincludegraphics{0.19\textwidth}{invader_step4.pdf} \\
\end{tabular}
\caption[Four first iterations of Alg.~\ref{algo::pardircollapse_v0}]{\label{fig::example_algo} \textbf{Four first iterations of Alg.~\ref{algo::pardircollapse_v0}} running on the left-most shape.}
\end{center}
\end{figure}

Different definitions of orientation and direction can be given, each corresponding to a different order of free faces removal in the complex and leading to different results.
Algorithm~\ref{algo::pardircollapse_v0} can be implemented to run in linear time complexity (proportionally to the number of faces in the complex). Indeed, checking if a face is free or not may be easily done in constant time and when a free pair $(f,g)$ is removed from the input complex, it is sufficient to scan the faces contained in $f$ in order to find new free faces.

\section{Aspect preservation during thinning}
\label{sec::aspect_no_param}
As previously said, our goal is to use the skeleton of the voids of a scene in order to guide light rays from the camera of the scene towards the light. Moreover, this skeleton needs to capture the main geometrical features of the original scene. For example, if the input is a corridor (the void of the corridor), then the skeleton should be a line following the main direction of the corridor.

@@

\begin{figure}[tb]
\begin{center}
\begin{tabular}{cccc}
	\myincludegraphics{0.22\textwidth}{fish.pdf} &
	\myincludegraphics{0.22\textwidth}{fishd.pdf} &
	\myincludegraphics{0.22\textwidth}{fishdd.pdf} &
	\myincludegraphics{0.22\textwidth}{fishcenter.pdf} \\
\end{tabular}
\caption[Example of opening and decenterness map]{\label{fig::globalopening} \textbf{Example of opening and decenterness map - } From left to right: a shape $S \subset \Zset^2$ (in gray), $\Dist1{S}$, $\DD1{S}$ and $\decent{S}$ (low values have dark colour).}
\end{center}
\end{figure}

\subsection{Parameter-free filtered thinning}
As previously said, we add edges to the set $W$ of Alg.~\ref{algo::pardircollapse_v0} in order to retain, in the resulting curvilinear skeleton, important edges from the original object. Given a cubical complex $X$, if an edge of $X$ has a high decenterness value for $X$, then it is probably located too close to the border of $X$ and does not represent an interesting geometrical feature to preserve.
On the other hand, if an edge has a high lifespan for $X$, then it means it was not removed quickly, after becoming a facet, by the thinning algorithm and might represent some precious geometrical information on the original object. An idea would be to keep, during thinning, all edges whose lifespan is superior to the decenterness value. Unfortunately, this strategy produces skeletons with many spurious branches in surfacic areas of the original object.

@@

\begin{algorithm}[tb]
\label{algo::3d_curvskel}
\caption[CurvilinearSkeleton]{$CurvilinearSkeleton(X)$}
\KwData{A cubical complex $\complex{3}{X}$}
\KwResult{A cubical complex $\complex{3}{Y}$}
\lnl{curvskel:01} $W=\{f \in X | \lifespan{f}{X} > \cpldecent{X}(f) + \birth{f}{X} - \cplDist1{X}(f)$ and $\mydim{f}=1\}$\;
\Return $ParDirCollapse(X,W,+\infty)$\;
\end{algorithm}

@@

Algorithm \ref{algo::3d_curvskel} allows to obtain a filtered curvilinear skeleton from a three dimensional complex. The results presented in Fig.~\ref{fig::result_skel} show that the skeletons contain the main geometrical information from the input shapes, and no spurious branch.

\begin{figure}[tb]
\begin{center}
\begin{tabular}{cc|cc}
	\myincludegraphics{0.18\textwidth}{hand2.jpg} &
	\myincludegraphics{0.18\textwidth}{hand_curvskel.jpg} &
	\myincludegraphics{0.24\textwidth}{neptune.jpg} &
	\myincludegraphics{0.24\textwidth}{neptune_curvskel.jpg} \\
\end{tabular}
\caption[Results of algorithm \ref{algo::3d_curvskel}]{\label{fig::result_skel} \textbf{Results of algorithm \ref{algo::3d_curvskel}} for two shapes: a hand (left) and a statue (right). In each pair, the rightmost image represents the skeleton.}
\end{center}
\end{figure}
